Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-14 paper/paper.tex
hscc17

The ADC and DAC may be abstracted by transforming the hybrid system in
Figure~\ref{fig:sampledsystem} into the digital system in
Figure~\ref{fig:digsystem1}, where the parametric uncertainties are
represented by~$\Delta_p \vec{G}$
%
%=\mathcal{Z}\left\lbrace{G_{P}(s)}\right\rbrace$
%
and the entire effect of $\nu_{1}$ and $\nu_{2}$ in the output $Y(z)$ is
represented as an additive (output) measurement noise~$\nu(z)$.
%, thus
%$\hat{Y}(z)=Y(z)+\nu(z)$.  The measurement noise $\nu(k)$ is enough for
%represent both quantisation noises ($\nu_{1}$ and $\nu_{2}$) what can be
%obtained reorganizing the equations~\ref{eq:outputfunctions}:
%%
%\begin{equation}
%\label{eq:outputfunctions2}
%\hat{Y}(z)=H_{1}R(z)+H_{1}\nu_{1}(z)+H_{2}(z)\nu_{2}(z),
%\end{equation}
%%
%where $H_{1}R(z)$ is exactly equal to $Y(z)$ without quantisation noise effects, thus:
%%
%\begin{equation}
%\nu(z)=H_{1}\nu_{1}(z)+H_{2}(z)\nu_{2}(z).
%\end{equation}

@@

%
In Figure~\ref{fig:digsystem1}, two sources of uncertainties are
illustrated: parametric uncertainties related to modelling errors, and
uncertainties introduced by quantisations in sampling and holding process,
i.e., ADC and DAC conversions.  Assuming linearity and independence between
these sources, the uncertain model may be rewritten as
%
\begin{equation}
\label{eq:complete_unc_model}
\vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}+\Delta_q \vec{G},
\end{equation}
%
where $\Delta_p \vec{G}$ is the term that corresponds to the parametric
uncertainties and $\Delta_q \vec{G}$ is the term that reflects the
quantisation effects on the plant model.

@@

Let $\hat{C}(z)$ be the transfer function of the digital controller
represented using this FWL with integer size $I$ and fractional size~$F$. 
We shall denote the FWL domain of coefficients as $\mathbb{R}\langle I,F
\rangle$
%
%Since the controller is implemented in the $\mathbb{R}\langle I,F \rangle$ 
%domain, {\it i.e.} a Fixed-Point Finite Word Length with integer size $I$ and fractional
%size $F$, we shall denote this domain as $\mathbb{R}\langle I,F \rangle$ 
%
and assume that there exists a function
$\mathit{FWL}[\cdot]:\mathcal{P}^{n}\rightarrow \mathcal{P}^{n}\langle I,F \rangle$,
which applies the FWL effects to a polynomial.  $\mathcal{P}^{n}$ is the
space of polynomials of $n$-th order and $\mathcal{P}^{n}\langle I,F
\rangle$ is is the space of polynomials with coefficients in
$\mathbb{R}\langle I,F \rangle$.
%
%, \red{[explain index n! why do you need to work on a Euclidean domain?]}. 
%
Thus, the perturbed controller model $\hat{C}(z)$ may be obtained from the
original model $C(z)=\frac{N_{C}(z)}{D_{C}(z)}$ as follows:
%
\begin{equation}
\hat{C}(z)=\frac{\mathit{FWL}[N_{C}(z)]}{\mathit{FWL}[D_{C}(z)]}.
\end{equation}
%
In the case of a synthesised controller, because the synthesis is performed
using FWL, $\hat{C}(z) \equiv C(z)$.

@@

The program synthesis engine uses fixed-point arithmetic.  Namely, we use
the domain $\mathbb{R}\param{I}{F}$ for the controller's coefficients and
the domain $\mathbb{R}\param{I_b}{F_b}$ for the plant's coefficients, 
where $I$ and $F$, as well as $I_b$ and $F_b$, denote the integer and
fractional size, respectively, and $\mathbb{R}\langle I_b,F_b \rangle
\supseteq \mathbb{R}\langle I,F \rangle$.
%
%the coefficients for $C(z)$ 
%$N_c$ and $D_c$ 
%in the domain $\mathbb{R}\param{I}{F}$, 
%and $\mathbb{R}^{m_C}\param{I}{F}$, respectively, 
%where $n_C$ and $m_C$ denote the order of the corresponding polynomials
%where $I$ and $F$ denote the integer and fractional size, respectively.
%Regarding the plant, its coefficients are this is synthesised over the 
%domain $\mathbb{R}^{n_G+m_G}\param{I_b}{F_b}$, where $n_G$ and $m_G$ 
%denote the order of the polynomials representing the 
%numerator and denominator of the plant's transfer function, respectively. 
%Again, $I_b$ and $F_b$ denote the integer and fractional size, respectively, with
%$\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.

@@

The median runtime for our benchmark set is $197$\,s, implying that half of
the controllers can be synthesised in less than $5$ minutes using our
present approach.  Overall, the average synthesis time amounts to
approximately $30$ minutes.  With respect to RQ2 we consider these times
short enough to be of practical use to control engineers.  Regarding RQ1 we
further conclude that the approach using a two-stage verification engine is
able to synthesise stable controllers in the $12$ out of $15$ benchmarks,
and can be complemented using the one-stage engine for $2$ additional
benchmarks, where the inductive conjectures fail.  Both verification engines
together enabled controller synthesis for $14$ out of $15$ benchmarks.  For
the $1$ remaining benchmark our approach failed to synthesise a stable
controller in the requested time limits.  This can be addressed by either
increasing the fixed point word widths considered or using floating point
arithmetic instead.  A link to the full experimental environment, including
scripts to reproduce the results, all benchmarks and the DDSynth tool, is
provided in the
footnote.\footnote{\url{https://drive.google.com/file/d/0ByIexo3Z5N91QkhrMi1rdkZFTWc/view}}

>>>>

The ADC and DAC may be abstracted by transforming the closed-loop system in
Figure~\ref{fig:sampledsystem} into the digital system in 
Figure~\ref{fig:digsystem1}, where the parametric uncertainties are
represented by~$\Delta_p \vec{G}$
%
%=\mathcal{Z}\left\lbrace{G_{P}(s)}\right\rbrace$
%
and the entire effect of $\nu_{1}$ and $\nu_{2}$ in the output $Y(z)$ is
represented as an additive output noise~$\nu(z)$. 
%, thus
%$\hat{Y}(z)=Y(z)+\nu(z)$.  The measurement noise $\nu(k)$ is enough for
%represent both quantisation noises ($\nu_{1}$ and $\nu_{2}$) what can be
%obtained reorganizing the equations~\ref{eq:outputfunctions}:
%%
%\begin{equation}
%\label{eq:outputfunctions2}
%\hat{Y}(z)=H_{1}R(z)+H_{1}\nu_{1}(z)+H_{2}(z)\nu_{2}(z),
%\end{equation}
%%
%where $H_{1}R(z)$ is exactly equal to $Y(z)$ without quantisation noise effects, thus:
%%
%\begin{equation}
%\nu(z)=H_{1}\nu_{1}(z)+H_{2}(z)\nu_{2}(z).
%\end{equation}

@@

%
In Figure~\ref{fig:digsystem1}, two sources of uncertainties are
illustrated: parametric uncertainties related to modelling errors, and
uncertainties introduced by quantisations in sampling and holding process,
i.e., ADC and DAC conversions.  Assuming linearity and independence between
these sources, the uncertain model may be rewritten as 
\red{[unclear whether this is over the s or z domain. further there is lack of proper subscripts (n,d,s), as per the notations introduced above.]}
%
\begin{equation}
\label{eq:complete_unc_model}
\vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}+\Delta_q \vec{G},
\end{equation}
%
where $\Delta_p \vec{G}$ is the term that corresponds to the parametric
uncertainties and $\Delta_q \vec{G}$ is the term that reflects the
quantisation effects on the plant model.

@@

Let $\hat{C}(z)$ be the transfer function of the digital controller
represented using this FWL with integer size $I$ and fractional size~$F$. 
We shall denote the FWL domain of coefficients as $\mathbb{R}\langle I,F
\rangle$
%
%Since the controller is implemented in the $\mathbb{R}\langle I,F \rangle$ 
%domain, {\it i.e.} a Fixed-Point Finite Word Length with integer size $I$ and fractional
%size $F$, we shall denote this domain as $\mathbb{R}\langle I,F \rangle$ 
%
and assume that there exists a function
$\mathit{FWL}[\cdot]:\mathcal{P}^{n}\rightarrow \mathcal{P}^{n}\langle I,F \rangle$,
which applies the FWL effects to a polynomial.  
\red{above $\mathcal{P}$ was defined as a single polynomial, now it is a space of polynomials. actually space of polynomials form specific algebraic structures, called diods -- we should have used those ... }
$\mathcal{P}^{n}$ is the
space of polynomials of $n$-th order and $\mathcal{P}^{n}\langle I,F
\rangle$ is is the space of polynomials with coefficients in
$\mathbb{R}\langle I,F \rangle$.
%
%, \red{[explain index n! why do you need to work on a Euclidean domain?]}. 
%
\red{[above you introduced a notation for poly ratios, which now you do not use?]}
Thus, the perturbed controller model $\hat{C}(z)$ may be obtained from the
original model $C(z)=\frac{N_{C}(z)}{D_{C}(z)}$ as follows:
%
\begin{equation}
\hat{C}(z)=\frac{\mathit{FWL}[N_{C}(z)]}{\mathit{FWL}[D_{C}(z)]}.
\end{equation}
%
In the case of a synthesised controller, because the synthesis is performed
using FWL, $\hat{C}(z) \equiv C(z)$.

@@

The program synthesis engine uses fixed-point arithmetic.  Namely, we use
the domain $\mathbb{R}\param{I}{F}$ for the controller's coefficients and
the domain $\mathbb{R}\param{I_b}{F_b}$ for the plant's coefficients.  Note
that $I$ and $F$, as well as $I_b$ and $F_b$, denote the integer and
fractional size, respectively, with $\mathbb{R}\langle I_b,F_b \rangle
\supseteq \mathbb{R}\langle I,F \rangle$.
%
%the coefficients for $C(z)$ 
%$N_c$ and $D_c$ 
%in the domain $\mathbb{R}\param{I}{F}$, 
%and $\mathbb{R}^{m_C}\param{I}{F}$, respectively, 
%where $n_C$ and $m_C$ denote the order of the corresponding polynomials
%where $I$ and $F$ denote the integer and fractional size, respectively.
%Regarding the plant, its coefficients are this is synthesised over the 
%domain $\mathbb{R}^{n_G+m_G}\param{I_b}{F_b}$, where $n_G$ and $m_G$ 
%denote the order of the polynomials representing the 
%numerator and denominator of the plant's transfer function, respectively. 
%Again, $I_b$ and $F_b$ denote the integer and fractional size, respectively, with
%$\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.

@@

The median runtime for our benchmark set is $197$\,s, implying that half of
the controllers can be synthesised in less than $5$ minutes using our
present approach.  Overall, the average synthesis time amounts to
approximately $30$ minutes.  With respect to RQ2 we consider these times
short enough to be of practical use to control engineers.  Regarding RQ1 we
further conclude that the approach using a two-stage verification engine is
able to synthesise stable controllers in the $12$ out of $15$ benchmarks,
and can be complemented using the one-stage engine for $2$ additional
benchmarks, where the inductive conjectures fail.  Both verification engines
together enabled controller synthesis for $14$ out of $15$ benchmarks.  For
the $1$ remaining benchmark our approach failed to synthesise a stable
controller in the requested time limits.  This can be addressed by either
increasing the fixed point word widths considered or using floating point
arithmetic instead.  A link to the full experimental environment, including
scripts to reproduce the experiment, all benchmarks and the DDSynth tool is
provided in the
footnote.\footnote{\url{https://drive.google.com/file/d/0ByIexo3Z5N91QkhrMi1rdkZFTWc/view}}
